Dealing with Consumer Uncertainty: Online Consumer Reviews and What makes them helpful?

### 2022-12-17 Paper.Rmd
final draft complete

---
documentclass: report
title: 'Dealing with Consumer Uncertainty: Online Consumer Reviews and What makes them helpful?'
bibliography: references.bib
csl: apa.csl
toc: no
link-citations: yes
output:
  bookdown::pdf_document2:
    fig.caption: yes
    includes:
      in_header: [non-float-fig.tex, custom.tex]
    toc_depth: 4
geometry: left=40mm, right=20mm, top=30mm, bottom=30mm
fontsize: 12pt
papersize: A4
linestretch: 1.5
fontfamily: times
---

@@

@@

@@

Since OCR do not share the same level of informativeness and usefulness [@pan2011], most of the electronic retail websites implemented a very well known "helpfulness" feature to their customer review systems in order to help their customers navigate through thousand of reviews. On some websites, this feature is implemented in a way that *helpful* / *unhelpful* buttons are present and on some other websites, there is only a *helpful* button. In this study, the data was acquired from websites which support *helpful* / *unhelpful* system since it was found that helpfulness as a percentage (helpful votes over total votes) creates more powerful results than considering only helpful votes as a count variable [@ahmad2015].

@@

Many different independent variables and their relationship between perceived helpfulness were examined by researchers. @hong2017 groups these independent variables into two chunks. The first group is reviewer-related predictors. Variables within this group try to understand the relationship between reviewer status (reviewer expertise, number of past reviews etc.) and perceived helpfulness. [@sun2019; @ghose2011]. The second group tries to understand the review-related relationships such as review length, review extremity, discrete review emotion etc. [@mudambi2010; @ghose2011; @ren2019; @eslami2018]. @ghose2011 showed that review-related predictors have stronger prediction power than reviewer-related ones. It should be noted that these two groups are not mutually exclusive and can be employed in the same study. The choice of the variables is heavily dependent on the data itself. In this particular study, only review-related predictors were examined because the data which is available for this study only allows for review-related variables. Reviewer-related variables could not be employed because IMDB and BestBuy use different conventions to identify their users(reviewers).

Review Length (Depth) could be considered as one of the most important independent variable explaining the perceived helpfulness. It might be implemented in different ways but for the majority of the studies it is the word count in a given review. For the most of the researchers, longer reviews contain more information about the product. As the potential buyer gets more information from a single review, he decreases his search costs with minimum effort [@mudambi2010; @hong2017; @liu2014; @wang2018; @korfiatis2012; @lee2016; @lee2014; @choi2020]. However, other group of researchers found out that there was a threshold on review length, meaning unnecessarily long reviews might have useless information in them[@schindler2012; @huang2015]. Another group indicates the word count of the review shows diminishing returns to helpfulness, supporting the threshold idea [@baek2012; @kuan2015; @eslami2018]. Although very rare, a negative relationship between Review Length and Perceived Helpfulness was also reported [@chatterjee2020; @yang2019].

@@

Many different types of research methodologies were employed in the literature of the Review Helpfulness. To my knowledge the most common empirical analysis method that was used in the literature was Tobit Regression because of the limited and censored nature of the Reviews Helpfulness [@mudambi2010; @korfiatis2012; @huang2015; @choi2020; @ren2019; @chua2014]. Some of these studies also shared Ordinary Least Squares results alongside with the Tobit Regression results for the purpose of benchmarking [@mudambi2010; @kuan2015; @choi2020]. Ordinary Least Squares were also used as a main empirical methodology in some papers [@liu2014; @ghose2006; @lee2016]. Furthermore, Ordinary Least Squares was employed in a hierarchical manner as well [@baek2012]. Some other studies employed Multi-Level Regression model in order to deal with the potential selection bias which is present in the data [@ghose2011; @wu2021; @kuan2015]. In a rare case Ordinal Logistic Regression was one of the methods that was used to explain the determinants of the review helpfulness [@cao2011]. Predictive methods such as Neural Networks were used to understand the components of a helpful review as well [@lee2014]. One paper attacked the problem of the review helpfulness with three methods, specifically, Partial Least Squares - Structural Equation Modelling, ANOVA Analysis and Artificial Neural Networks [@eslami2018].

@@

Relaxing the assumption that consumers have perfect information about the products on the market raises the problem of information acquisition for consumers. Getting the complete information about products is important because economic agents want to maximize their utility by finding the best good with respect to their budget constraints on the market. The complete information is the information about both the prices and quality levels of the goods which are available on the market. Acquiring the information about the quality of a product is harder than getting the information about its price. To explain, a consumer can check the price list of laptops and have an idea about the maximum and the minimum prices but getting the information about a laptop's technical components or a brand's support for its products is a lot more effort taking and costly.

In order to solve this problem @nelson1970 differentiated goods based on their search and experience attributes [@nelson1974economic; @nelson1974; @nelson1981]. Search Attributes are the qualities that can be assessed before purchase. On the contrary, Experience Attributes can only be assessed by using the product itself, in other words, evaluation is only possible after purchase. A single good can have both search and experience attributes. Depending on its dominant attributes the good can be classified as Search or Experience. @darby1973 extended Search and Experience goods framework with Credence goods where consumers can not evaluate the good even after the consumption. Though, Credence goods will not be discussed any further in this study.

@@

@nelson1970 also states that consumers can use other consumers' experiences in their search processes. The information about a certain good is usually acquired in the form of "word-of-mouth" in this kind of search process. This type of search is viable when getting the information about a certain product is much more costly by "experience" compared to by "search", i.e., sampling the product is very costly. For instance buying a laptop and trying to figure out if it is the best laptop for a certain task may even require buying additional laptops because of the need for comparison. This is the way of "experiencing" the good and this would be very costly. On the other hand, the potential buyer may want to hear from people who do the similar tasks with their laptops and try to sort out the best possible laptop model for her own task. This way she gets information about the product without having to "experience" it and this approach is way cheaper.

@@

The data was scraped with a custom web scraper which was constructed with Selenium Framework for Python 3 [@python3]. The scraper aqcuired the customer reviews from IMDB and BestBuy. The former is the biggest platform for Movies and TV Shows, the latter is one of the biggest electronic retailers in United States of America. Both websites host a great amount of online reviews. After the data was collected it was further transformed and analyzed with the help of R Programming Language [@RCore; @Tidyverse; @Tidytext].

@@

@hong2014 states that consumers likely to form uniform opinions about search goods [@sun2019]. On the contrary, the same paper suggests that consumers' opinions are more diversified on experience goods. Intuitively, what these histograms show is the same. For instance, positive or negative attributes of search goods can be expressed in a limited number of ways. The storage space of a phone might be small or CPU of a laptop might not be fast as expected. Thus, one good review is enough to reveal the quality of a product. This might be the reason why such a big spike at 100% was observed on Figure \@ref(fig:IV-Hist-Search). In the movies (experience good) case on Figure \@ref(fig:IV-Hist-Exp), it can be seen that readers usually disagree with each other because the distribution of the perceived helpfulness distributed around 50%. This might be because evaluation process of movies is rather subjective. For instance, one person might not like Spider-Man: Homecoming and another would love it. This might depend on how a person idealizes the Spider-Man or Peter Parker image in her mind which is completely subjective.

@@

On scatter plots (see Figure \@ref(fig:Search-Pos) (B) and Figure \@ref(fig:Experience-Pos) (B)), relationships between perceived helpfulness and proportion of positive words are looking very similar to their negative counterparts. Furthermore, these plots kind of similar to perceived helpfulness versus number of words plots (see Figure \@ref(fig:Search-Length) (B) and Figure \@ref(fig:Experience-Length) (B)). In a sense, both negative and positive proportions imply number of words. As the proportion increases so does the number of words. That is why aforementioned figures show similar relationships between variables. On higher dimensions these relationships might be different. That is why Exploratory Data Analysis should never be conducted in a confirmatory sense.

@@

In order to decrease the uncertainty in the most optimal way, search costs must be reduced. In Section \@ref(search-and-experience-goods-classification) it was mentioned that the action of search was costlier for Experience Goods than Search Goods. Furthermore, people tend to have similar opinions about Search Goods [@hong2014]. This might mean that information cues are much more uniform for Search Goods [@huang2015; @baek2012]. In other words, there are limited ways to construct a review because search attributes are more objective. Therefore, there might be a positive linear relationship between Perceived Helpfulness and Review Length because longer reviews can help the consumers in their decision making process by increasing the amount of information they have. However, since the attributes of electronics are objectively identifiable and limited (e.g., storage space of a phone, RAM of a laptop, color depth of a TV etc.) there are not much to review for a reviewer. Because of this, there might be diminishing marginal returns to Review Length. After some point more information can cause confusion and may render the review unfocused [@schindler2012; @huang2015]. On the contrary, for Experience Goods, people have tendency to form heterogeneous opinions [@hong2014]. This means that movie reviews are much more subjective by nature. Since there are less objectivity, a helpful review to one person might not be helpful to another. This might decrease the average responsiveness of the Perceived Helpfulness to the Review Length. However, since there are other ways to objectively evaluate a movie such as quality of its effects, its budget and how well this budget is utilized, a weaker positive linear relationship is expected. Therefore it is hypothesized that:

@@

So far it should be understood that people try to cut down their losses. That is why negative cues draw more attention than positive ones [@kahneman1979; @schindler2017]. Additionally, people find negative information more credible and persuasive than positive information [@ito1998; @Kanouse1984ExplainingNB]. It is known that Review Rating is the satisfaction level of a customer towards a product. However, Review Rating itself is not enough to convey the information about how a customer expresses her satisfaction / dissatisfaction towards a product. The way a customer expresses her opinion on a product might have an effect on the perceived helpfulness of a review. Reviews with negative sentiments may bring out the risks associated with the purchase better than reviews with positive sentiments. Since in this study movies and electronics are compared, it is costlier to make a wrong decision on Search Goods than Experience Goods. Therefore, it is hypothesized that:

@@

Tobit Regression is selected as the analysis method because of three reasons. First of all, the dependent variable, perceived helpfulness, is defined in a continuous range from 0 to 1 since perceived helpfulness is a percentage as mentioned above. The second reason as stated by @mudambi2010 is the potential selection bias in the sample. Unfortunately, it is not possible to know how many people read a particular review. Neither BestBuy nor IMDB disclose this information. Because of this, being included in a sample could be correlated with independent variables. For instance, potentially more voted reviews could attract more readers or readers could be drawn to reviews which have certain ratings. Lastly, there are many studies from the literature that used Tobit Regression as their research method [@mudambi2010; @korfiatis2012; @huang2015; @choi2020; @ren2019].

@@

A positive linear relationship between the logarithm of Review Length and Perceived Helpfulness was proposed with Hypothesis 2. A strong relationship between Review Length and Perceived Helpfulness is observed (0.404, p \< 0.001) for Search Goods. This effect is moderated by Review Extremity since the interaction effect is significant with a negative sign (-0.043, p \< 0.001). As review rating increases the responsiveness of the Perceived Helpfulness to Review Length decreases. This means that for positive extreme reviews relatively shorter texts are more helpful. Logarithmic form also proves that additional words in a review shows diminishing returns to helpfulness. Experience Goods somewhat deviates from the results of Search Goods. There is a weak positive relationship between Review Length and Perceived Helpfulness (0.021, p \< 0.01). However, this positive relationship quickly turns to negative for higher ratings because of the presence of the interaction term between Review Length and Review Extremity (-0.015, p \< 0.001). For lower ratings Hypothesis 2 is fully supported but as the Review Extremity increases this support weakens.

@@

Negativity Bias Theorem and Prospect Theory had a strong support in the case of search goods. The regression results showed that the reviews which had low ratings and/or reviews which had more negative words in them were found to be more helpful on the average. Additionally, Perceived Helpfulness has higher responsiveness to Review Length when a review has a low rating. This means that people focus more on negative cues than positive cues because the marginal value of additional negative information is higher. This way consumers are able to cut down potential sure losses. A similar result was reflected by the negative coefficient of the proportion of positive words in a review. This shows that reviews with positive sentiments do not offer diagnostic value for consumers. Nonetheless, the U-Shape of the Review Rating variable also suggests positivity bias [@hoorens2014]. An explanation to this could be that certain brands or products might be favored by some customers and these customers might selectively tend towards positively rated reviews and find them helpful just because they love the brand [@zhu2021]. The reason why there is a divergence between the "positively rated review" and "a review with positive sentiment" might be explained by this. A consumer who has brand or product inclinations wants to be persuaded to have the product so this particular consumer does not really care about what is written in the review, he might skim through positive reviews until he feels persuaded. Since a preference towards a brand is subjective it might be speculated that a strong brand image could embed experience attributes into search goods. A similar notion was discussed by @mudambi2010 where they classified Apple iPod as an experience good. That is although an MP3 player such as iPod has many objective search attributes such as storage capacity and battery life, what makes this particular product preferable most of the time is the product image that was created by Apple.

@@

Secondly, as pointed out in Section \@ref(literature-review), there were many different research designs present in the literature. Let alone different methodologies, even the utilizations of similar variables were contrasting. For instance, review extremity was employed in three different ways by researchers. This study and some others use the review ratings as it is. Another group of studies took the differences of review ratings from the mean rating of a given product. The resulting variable is usually called Review Inconsistency. The last group of researchers utilized a dummy variable for neutral reviews (3 out of 5) and extreme reviews (1,2,4,5 out of 5). In some studies these dummy variables were extended to negative and positive extreme dummies as well. The differences are not limited to Review Rating. The usages the dependent variable, Perceived Helpfulness, diverged as well. In some circumstances only absolute Helpful votes were used along with Negative Binomial Regression. Furthermore, some studies converted the percentage of the helpfulness into a binary problem where reviews with over 50% helpfulness score was considered as a helpful review. As a last example to different applications, scale transformations (logarithmic transformation, etc.) were applied liberally as well. All in all, it is clear that there is no standard approach in the literature which might be the reason why there are many conflicting results.

@@

With this way consumers would be able to purchase the best good available in the market with respect to their budgets, i.e., maximizing their utilities. This collective behavior may even impact social welfare positively since economic agents are making much more informed decisions. Unfortunately, similar implications can not be made for experience goods, specifically for movies, since the realized results were mostly different that what was hypothesized. Thus, this study can not offer any suggestions for movie reviews.

There are some implications for the future studies. Firstly, aside from lexicon based sentiment analysis it is also possible to utilize deep learning methods to mine opinions from a text. One advantage of deep learning method over a lexicon is its versatility. A negative word can change from one context to another and training a deep learning method is more robust to this type of contextual changes whereas with lexicon based methods a negative word is a negative word no matter the context is. Next, future studies should consider collecting data from different regions and cultures. There might be some differences on how consumers process and react to the information in order to deal with uncertainty. Additionally, researchers can dig deeper into search and experience goods paradigm. It is well established in the literature that product type affects the information gathering process. However, there might be differences within product types depending on their search and experience attributes. An objective way to identify and index experience and search attributes may also shed some light to the conflicting results in the literature. Lastly, since Online Consumer Reviews data is ever growing more researchers should incorporate Exploratory Data Analysis into their works. Reviews and how helpful these reviews are perceived by potential buyers is relatively a new topic. In addition, new ways to analyze text data are being developed since the area of Natural Language Processing is quite hot so Online Consumer Reviews offer a great potential for new discoveries from the data for different domains. This increases the value of the Exploratory Data Analysis as well.

>>>>

---
documentclass: report
bibliography: references.bib
csl: apa.csl
lof: no
lot: no
toc: no
link-citations: yes
output:
  bookdown::pdf_document2:
    fig.caption: yes
    includes:
      in_header: [non-float-fig.tex, custom.tex]
    toc_depth: 4
geometry: left=40mm, right=20mm, top=30mm, bottom=30mm
fontsize: 12pt
papersize: A4
linestretch: 1.5
fontfamily: times
---

@@

#title: 'Dealing with Consumer Uncertainty: Online Consumer Reviews and What makes #them helpful?'

@@

\setcounter{page}{1}

@@

Since OCR do not share the same level of informativeness and usefulness [@pan2011], most of the electronic retail websites implemented a very well known "helpfulness" feature to their customer review systems in order to help their customers navigate through thousands of reviews. On some websites, this feature is implemented in a way that *helpful* / *unhelpful* buttons are present and on some other websites, there is only a *helpful* button. In this study, the data was acquired from websites which support *helpful* / *unhelpful* system since it was found that helpfulness as a percentage (helpful votes over total votes) creates more powerful results than considering only helpful votes as a count variable [@ahmad2015].

@@

Many different independent variables and their relationship between perceived helpfulness were examined by researchers. @hong2017 groups these independent variables into two chunks. The first group is reviewer-related predictors. Variables within this group try to understand the relationship between reviewer status (reviewer expertise, number of past reviews etc.) and perceived helpfulness. [@sun2019; @ghose2011]. The second group tries to understand the review-related relationships such as review length, review extremity, discrete review emotion etc. [@mudambi2010; @ghose2011; @ren2019; @eslami2018]. @ghose2011 showed that review-related predictors have stronger prediction power than reviewer-related ones. It should be noted that these two groups are not mutually exclusive and can be employed in the same study. The choice of the variables is heavily dependent on the data itself. In this particular study, only review-related predictors were examined because the data which is available for this study only allows for review-related variables. Reviewer-related variables could not be employed because IMDB and BestBuy use different conventions to identify their users (reviewers).

Review Length (Depth) could be considered as one of the most important independent variable explaining the perceived helpfulness. It might be implemented in different ways but for the majority of the studies it is the word count in a given review. For the most of the researchers, longer reviews contain more information about the product. As the potential buyer gets more information from a single review, he decreases his search costs with minimum effort so the amount of information (words) that a review contains becomes very important. [@mudambi2010; @hong2017; @liu2014; @wang2018; @korfiatis2012; @lee2016; @lee2014; @choi2020]. However, other group of researchers found out that there was a threshold on review length, meaning unnecessarily long reviews might have useless information in them[@schindler2012; @huang2015]. Another group indicates the word count of the review shows diminishing returns to helpfulness, supporting the threshold idea [@baek2012; @kuan2015; @eslami2018]. Although very rare, a negative relationship between Review Length and Perceived Helpfulness was also reported [@chatterjee2020; @yang2019].

@@

Many different types of research methodologies were employed in the literature of the Review Helpfulness. To my knowledge the most common empirical analysis method that was used in the literature was Tobit Regression because of the limited and the censored nature of the Reviews Helpfulness [@mudambi2010; @korfiatis2012; @huang2015; @choi2020; @ren2019; @chua2014]. Some of these studies also shared Ordinary Least Squares results alongside with the Tobit Regression results for the purpose of benchmarking [@mudambi2010; @kuan2015; @choi2020]. Ordinary Least Squares were also used as a main empirical methodology in some papers [@liu2014; @ghose2006; @lee2016]. Furthermore, Ordinary Least Squares was employed in a hierarchical manner as well [@baek2012]. Some other studies employed Multi-Level Regression model in order to deal with the potential selection bias which is present in the data [@ghose2011; @wu2021; @kuan2015]. In a rare case Ordinal Logistic Regression was one of the methods that was used to explain the determinants of the review helpfulness [@cao2011]. Predictive methods such as Neural Networks were used to understand the components of a helpful review as well [@lee2014]. One paper attacked the problem of the review helpfulness with three methods, specifically, Partial Least Squares - Structural Equation Modelling, ANOVA Analysis and Artificial Neural Networks [@eslami2018].

@@

Relaxing the assumption that consumers have perfect information about the products on the market raises the problem of information acquisition for consumers. Getting the complete information about products is important because economic agents want to maximize their utility by finding the best good with respect to their budget constraints on the market. The complete information is the information about both the prices and the quality levels of the goods which are available on the market. Acquiring the information about the quality of a product is harder than getting the information about its price. To explain, a consumer can check the price list of laptops and have an idea about the maximum and the minimum prices but getting the information about a laptop's technical components or a brand's technical support for its products is a lot more effort taking and costly.

In order to solve this problem @nelson1970 differentiated goods based on their search and experience attributes [@nelson1974economic; @nelson1974; @nelson1981]. Search Attributes are the qualities that can be assessed before purchase. On the contrary, Experience Attributes can only be assessed by using the product itself, in other words, evaluation is only possible after purchase. A single good can have both search and experience attributes. Depending on its dominant attributes the good can be classified as Search or Experience. Thus, search and experience classification is not usually a clear cut one, rather it could be considered as a spectrum. @darby1973 extended Search and Experience goods framework with Credence goods where consumers can not evaluate the good even after the consumption. Though, Credence goods will not be discussed any further in this study.

@@

@nelson1970 also states that consumers can use other consumers' experiences in their search processes. The information about a certain good is usually acquired in the form of "word-of-mouth" with this kind of search process. This type of search is viable when getting the information about a certain product is much more costly by "experience" compared to by "search", i.e., sampling the product is very costly. For instance buying a laptop and trying to figure out if it is the best laptop for a certain task may even require buying additional laptops because of the need for comparison. This is the way of "experiencing" the good and this would be very costly. On the other hand, the potential buyer may want to hear from people who do the similar tasks with their laptops and try to sort out the best possible laptop model for her own task. This way she gets information about the product without having to "experience" it and this approach is way cheaper.

@@

The data was scraped with a custom web scraper which was constructed with Selenium Framework for Python 3 [@python3]. The scraper acquired the customer reviews from IMDB and BestBuy. The former is the biggest platform for Movies and TV Shows, the latter is one of the biggest electronic retailers in United States of America. Both websites host a great amount of online reviews. After the data was collected it was further transformed and analyzed with the help of R Programming Language [@RCore; @Tidyverse; @Tidytext].

@@

@hong2014 states that consumers likely to form uniform opinions about search goods [@sun2019]. On the contrary, the same paper suggests that consumers' opinions are more diversified on experience goods. Intuitively, what these histograms show is the same. For instance, positive or negative attributes of search goods can be expressed in a limited number of ways. The storage space of a phone might be small or CPU of a laptop might not be fast as expected. Thus, one good review is enough to reveal the quality of a product. This might be the reason why such a big spike at 100% was observed on Figure \@ref(fig:IV-Hist-Search). In the movies (experience good) case on Figure \@ref(fig:IV-Hist-Exp), it can be seen that readers usually disagree with each other because the observations of the perceived helpfulness distributed around 50%. This might be because evaluation process of movies is rather subjective. For instance, one person might not like Spider-Man: Homecoming and another would love it. This might depend on how a person idealizes the Spider-Man or Peter Parker image in her mind which is completely subjective.

@@

On scatter plots (see Figure \@ref(fig:Search-Pos) (B) and Figure \@ref(fig:Experience-Pos) (B)), relationships between perceived helpfulness and proportion of positive words are looking very similar to their negative counterparts. Furthermore, these plots are kind of similar to perceived helpfulness versus number of words plots (see Figure \@ref(fig:Search-Length) (B) and Figure \@ref(fig:Experience-Length) (B)). In a sense, both negative and positive proportions imply the number of words. As the proportion increases so does the number of words. That is why aforementioned figures show similar relationships between variables. On higher dimensions these relationships might be different. That is why Exploratory Data Analysis should never be conducted in a confirmatory sense.

@@

In order to decrease the uncertainty in the most optimal way, search costs must be reduced. In Section \@ref(search-and-experience-goods-classification) it was mentioned that the action of search was costlier for Experience Goods than Search Goods. Furthermore, people tend to have similar opinions about Search Goods [@hong2014]. This might mean that information cues are much more uniform for Search Goods [@huang2015; @baek2012]. In other words, there are limited ways to construct a review because search attributes are more objective. Therefore, there might be a positive linear relationship between Perceived Helpfulness and Review Length because longer reviews can help the consumers in their decision making process by increasing the amount of information they have. However, since the attributes of electronics are objectively identifiable and limited (e.g., storage space of a phone, RAM of a laptop, color depth of a TV etc.) there are not much to review for a reviewer. Because of this, there might be diminishing marginal returns to Review Length. After some point more information can cause confusion and may render the review unfocused [@schindler2012; @huang2015]. On the contrary, for Experience Goods, people have tendency to form heterogeneous opinions [@hong2014]. This means that movie reviews are much more subjective by nature. Since there are less objectivity, a helpful review to one person might not be helpful to another. This might decrease the average responsiveness of the Perceived Helpfulness to the Review Length. However, since there are other ways to objectively evaluate a movie such as the quality of its effects, movie's budget and how well this budget was utilized, a weaker positive linear relationship is expected. Therefore it is hypothesized that:

@@

So far it should be understood that people try to cut down their losses. That is why negative cues draw more attention than positive ones [@kahneman1979; @schindler2017]. Additionally, people find negative information more credible and persuasive than positive information [@ito1998; @Kanouse1984ExplainingNB]. It is known that Review Rating is the satisfaction level of a customer towards a product. However, Review Rating itself is not enough to convey the information about how a customer expresses her satisfaction / dissatisfaction towards a product. The way a customer expresses her opinion about a product might have an effect on the perceived helpfulness of a review. Reviews with negative sentiments may bring out the risks associated with the purchase better than reviews with positive sentiments. Since in this study movies and electronics are compared, it is costlier to make a wrong decision on Search Goods than Experience Goods. Therefore, it is hypothesized that:

@@

Tobit Regression is selected as the analysis method because of three reasons. First of all, the dependent variable, perceived helpfulness, is defined in a continuous range from 0 to 1 since perceived helpfulness is a percentage as mentioned above. The second reason as stated by @mudambi2010 is the potential selection bias in the sample. Unfortunately, it is not possible to know how many people read a particular review. Neither BestBuy nor IMDB disclose this information. Because of this, being included in a sample could be correlated with independent variables. For instance, potentially more voted reviews could attract more readers or readers could be drawn to reviews which have certain ratings. Lastly, there are many studies from the literature that used Tobit Regression as their research methods [@mudambi2010; @korfiatis2012; @huang2015; @choi2020; @ren2019].

@@

A positive linear relationship between the logarithm of Review Length and Perceived Helpfulness was proposed with Hypothesis 2. A strong relationship between Review Length and Perceived Helpfulness is observed (0.404, p \< 0.001) for Search Goods. This effect is moderated by Review Extremity since the interaction effect is significant with a negative sign (-0.043, p \< 0.001). As review rating increases the responsiveness of the Perceived Helpfulness to Review Length decreases. This means that for positive extreme reviews relatively shorter texts are more helpful. Logarithmic form also proves that an additional word in a review shows diminishing returns to helpfulness. Experience Goods somewhat deviates from the results of Search Goods. There is a weak positive relationship between Review Length and Perceived Helpfulness (0.021, p \< 0.01). However, this positive relationship quickly turns to negative for higher ratings because of the presence of the interaction term between Review Length and Review Extremity (-0.015, p \< 0.001). For lower ratings Hypothesis 2 is fully supported but as the Review Extremity increases this support weakens.

@@

Negativity Bias Theorem and Prospect Theory had a strong support in the case of search goods. The regression results showed that the reviews which had low ratings and/or reviews which had more negative words in them were found to be more helpful on the average. Additionally, Perceived Helpfulness has higher responsiveness to Review Length when a review has a low rating. This means that people focus more on negative cues than positive cues because the marginal value of an additional negative information is higher. This way consumers are able to cut down potential sure losses. A similar result was reflected by the negative coefficient of the proportion of positive words in a review. This shows that reviews with positive sentiments do not offer diagnostic value for consumers. Nonetheless, the U-Shape of the Review Rating variable also suggests positivity bias [@hoorens2014]. An explanation to this could be that certain brands or products might be favored by some customers and these customers might selectively tend towards positively rated reviews and find them helpful just because they love the brand [@zhu2021]. The reason why there is a divergence between the "positively rated review" and "a review with positive sentiment" might be explained by this. A consumer who has brand or product inclinations wants to be persuaded to have the product so this particular consumer does not really care about what is written in the review, he might skim through positive reviews until he feels persuaded. Since a preference towards a brand is subjective it might be speculated that a strong brand image could embed experience attributes into search goods. A similar notion was discussed by @mudambi2010 where they classified Apple iPod as an experience good. That is although an MP3 player such as iPod has many objective search attributes such as storage capacity and battery life, what makes this particular product preferable most of the time is the product image that was created by Apple.

@@

Secondly, as pointed out in Section \@ref(literature-review), there were many different research designs present in the literature. Let alone different methodologies, even the utilizations of similar variables were contrasting. For instance, review extremity was employed in three different ways by researchers. This study and some others use the review ratings as it is. Another group of studies took the differences of review ratings from the mean rating of a given product. The resulting variable is usually called Review Inconsistency. The last group of researchers utilized a dummy variable for neutral reviews (3 out of 5) and extreme reviews (1,2,4,5 out of 5). In some studies these dummy variables were extended to negative and positive extreme dummies as well. The differences are not limited to Review Rating. The way the dependent variable was used, Perceived Helpfulness, diverged too. In some circumstances only absolute Helpful votes were used along with Negative Binomial Regression. Furthermore, some studies converted the percentage of the helpfulness into a binary problem where reviews with over 50% helpfulness score was considered as a helpful review. As a last example to different applications, scale transformations (logarithmic transformation, etc.) were applied liberally as well. All in all, it is clear that there is no standard approach in the literature which might be the reason why there are many conflicting results.

@@

With this way consumers would be able to purchase the best good available in the market with respect to their budgets, i.e., maximizing their utilities. This collective behavior may even impact social welfare positively since economic agents are making much more informed decisions. Unfortunately, similar implications can not be made for experience goods, specifically for movies, since the realized results were mostly different than what was hypothesized. Thus, this study can not offer any suggestions for movie reviews.

There are some implications for the future studies. Firstly, aside from lexicon based sentiment analysis it is also possible to utilize deep learning methods to mine opinions from a text. One advantage of the deep learning method over a lexicon is its versatility. A negative word can change from one context to another and training a deep learning method is more robust to this type of contextual changes whereas with lexicon based methods a negative word is a negative word no matter the context is. Next, future studies should consider collecting data from different regions and cultures. There might be some differences on how consumers process and react to the information in order to deal with uncertainty. Additionally, researchers can dig deeper into search and experience goods paradigm. It is well established in the literature that product type affects the information gathering process. However, there might be differences within product types depending on their search and experience attributes. An objective way to identify and index experience and search attributes may also shed some light to the conflicting results in the literature. Lastly, since Online Consumer Reviews data is ever growing more researchers should incorporate Exploratory Data Analysis into their works. Reviews and how helpful these reviews are perceived by potential buyers is relatively a new topic. In addition, new ways to analyze text data are being developed since the area of Natural Language Processing is quite hot so Online Consumer Reviews offer a great potential for new discoveries from the data for different domains. This increases the value of the Exploratory Data Analysis as well.
